An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-16 indicators/paper/paper.tex
No need for centering
Minor copyedits

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{fig/time_trends_national.pdf}
\caption{National trends, from April 2020 to April 2021, of four signals in
  the COVIDcast API. The auxiliary signals, based on medical claims data and
  massive surveys, track changes in officially reported cases quite
  well. (They have all been placed on the same scale as reported cases per
  100,000 people.)}
\label{fig:time_trends_national}
\end{figure}

@@

Figure~\ref{fig:geo_wise_correlation} shows the geo-wise correlations achieved
by the five signals and COVID case rates (from USAFacts, smoothed using a 7-day
trailing average), from April 15, 2020 to April 15, 2021. This calculation is
performed over counties with at least 500 cumulative cases by the end of this 
period, and at which all indicators are available (956 counties in total). The
significantly positive correlations suggest that these signals could be useful
in hotspot detection (identifying counties with relatively high COVID activity,
at a given time). Somewhat surprisingly, the survey-based CLI-in-community
signal shows the strongest correlations for much of the time period. This
clearly demonstrates the value of a large-scale survey such as CTIS for tracking
symptoms and case trends, especially when other data is unavailable.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{fig/bexar_compare.pdf}
\caption{Reported cases per day in Bexar County, Texas during the summer of
  2020. Only July 16, 4,810 backlogged cases were reported, though they
  actually occurred over the preceding two weeks (this shows up as a prolonged
  spike in the left panel due to the 7-day trailing averaging applied to the
  case counts). Daily CTIS estimates of CLI-in-community showed more stable
  underlying trends.}
\label{fig:bexar_compare}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
\caption{Estimated percentage of doctor's visits due to COVID-like illness
  displayed across multiple issue dates, with later issue dates adding
  additional data and revising past data from prior issue dates.}
\label{fig:dv_as_of}
\end{figure}

>>>>

% TODO: Cite this? https://arxiv.org/abs/2106.04420

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/time_trends_national.pdf}
\caption{National trends, from April 2020 to April 2021, of four signals in
  the COVIDcast API. The auxiliary signals, based on medical claims data and
  massive surveys, track changes in officially reported cases quite
  well. (They have all been placed on the same scale as reported cases per
  100,000 people.)}
\label{fig:time_trends_national}
\end{figure}

@@

Figure~\ref{fig:geo_wise_correlation} shows the geo-wise correlations achieved
by the five signals and COVID case rates (from JHU CSSE, smoothed using a 7-day
trailing average), from April 15, 2020 to April 15, 2021. This calculation is
performed over counties with at least 500 cumulative cases by the end of this
period, and at which all indicators are available (956 counties in total). The
significantly positive correlations suggest that these signals could be useful
in hotspot detection (identifying counties with relatively high COVID activity,
at a given time). Somewhat surprisingly, the survey-based CLI-in-community
signal shows the strongest correlations for much of the time period. This
clearly demonstrates the value of a large-scale survey such as CTIS for tracking
symptoms and case trends, especially when other data is unavailable.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/bexar_compare.pdf}
\caption{Reported cases per day in Bexar County, Texas during the summer of
  2020. Only July 16, 4,810 backlogged cases were reported, though they
  actually occurred over the preceding two weeks (this shows up as a prolonged
  spike in the left panel due to the 7-day trailing averaging applied to the
  case counts). Daily CTIS estimates of CLI-in-community showed more stable
  underlying trends.}
\label{fig:bexar_compare}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
\caption{Estimated percentage of doctor's visits due to COVID-like illness
  displayed across multiple issue dates, with later issue dates adding
  additional data and revising past data from prior issue dates.}
\label{fig:dv_as_of}
\end{figure}
